Models of lens candidates from Space Warps CFHTLS

### 2017-02-10 parts/figures.tex
clean up all images
bash magic rename
fix figures
add input images with scalebar, fixes#4
editing
editing text

\def\pwidth{.32\linewidth}

\def\includeten#1#2{
\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
}

\def\includezehn#1#2{
\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
}

\begin{figure*}
\includeten{spaghetti/}{_input}
\caption{Marked-up images. \label{fig:markedup}}
\end{figure*}

\begin{figure*}
\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
\caption{\label{fig:arriv}}
\end{figure*}

\begin{figure*}
\includeten{img/nsynth/}{_nsynth}
\label{fig:synth}
\caption{}
\end{figure*}

\begin{figure*}
\includezehn{img/kappa_map/}{_kappa_map}
\caption{\label{fig:kappa}}
\end{figure*}

\begin{figure*}
\includezehn{img/kappa_encl/}{_kappa_encl}
\caption{}
\end{figure*}

@@

>>>>

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time.  The curves
  help guide the placement of the dots, but their precise appearance
  has no significance.  This selection includes the best-modelled
  systems, but also one case (SW57 at upper right) of unsuccessful
  modelling. \label{fig:splinput}}
\end{figure*}

\begin{figure*}
\inclGrid{arrival_spaghetti}
\caption{Arrival-time surfaces of the candidates from
  Figure~\ref{fig:splinput}.
  \label{fig:arriv}}
\end{figure*}

\begin{figure*}
\inclGrid{nsynth}
\caption{Synthetic images of the systems from
  Figures~\ref{fig:splinput}--\ref{fig:arriv}.
  \label{fig:synth}}
\end{figure*}

\begin{figure*}
\inclGrid{kappa_map_interpol}
\caption{Mass distribution $\kappa$ in the systems from
  Figures~\ref{fig:splinput}--\ref{fig:synth}.
  \label{fig:kappa}}
\end{figure*}

\begin{figure*}
\inclGrid{kappa_encl}
\caption{Enclosed mass $\kappa$ in the systems from
  Figures~\ref{fig:splinput}--\ref{fig:kappa}.
  \label{fig:encl}}
\end{figure*}

@@

\begin{table*}
  \caption{Categorisation of SW models}
  \label{tab:models}
  \include{table}
\end{table*}

### 2017-02-10 parts/intro.tex
editing text

Purpose is twofold.  First, see if plausible mass models can produce
the overall configuration.  Second, interpretation as lensing
galaxies.  Introduce some diagnostics.

Each lens candidates in practice gets modelled several times in a
collaborative refinement process.\footnote{See ``Collaborative
  gravitational lens modelling\dots'' in {\tt
    http://letters.zooniverse.org} especially the model tree.}  This
representing a consensus among modellers, as to the best that could be
achieved with the available data and software.\footnote{This is in
  contrast to the main Space~Warps project for discovering lenses, in
  which volunteers in a crowd of $\gtrsim10^4$ make independent
  contributions.  Each person is presented with a random selection of
  survey-patches and invited to (in effect) vote on each.  The system
  estimates each volunteer's skill level according to test-patches
  interspersed with the real data, and weights their votes accordingly
  \citep{2016MNRAS.455.1171M}.  There is an active forum for
  volunteers, but since everyone is seeing different data samples with
  minimal overlap, the forum has little if any influence on votes.}

\begin{itemize}
\item Section~\ref{sec:morph} discusses nine of the systems, including
  six systems we found to be particularly interesting.  Morphology
  from Figure~\ref{fig:markedup}.
\begin{itemize}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  SW28), SQ for short-axis quads (as in Figure~SW02,
  SW09, SW29, SW42), IQ for inclined quads
  (as in Figure~SW05) and CQ for very symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~SW05 and SW42) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~SW58,
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Section~\ref{sec:massmodels}
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  For SW36 the model implies extra images or a long arc,
  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
\end{itemize}
\item Section~\ref{sec:stellar-mass} explains how we compare the lensing
mass with the mass in stars in the lensing galaxy.  We estimate the
stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
with the well-known stellar-population models of
\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
a halo mass using the abundance-matching prescription of
\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
than the stellar mass but no more than the total halo mass.  We then
introduce what we call a halo index $\haloindex$ which gives an idea
of how the lensing mass compares with these two bounds.
Figure~\ref{fig:stelmass}.
\end{itemize}

In this paper we report the most recent model for each lens, as

Section~\ref{sec:summary} builds Table~\ref{tab:models}.
The online supplement gives results for all the modelled systems.

>>>>

Purpose is twofold.  First, see if plausible mass models can produce
the overall configuration.  Second, interpretation as lensing
galaxies.

Each lens candidates in practice gets modelled several times in a
collaborative refinement process.  This represents a consensus among
modellers, as to the best that could be achieved with the available
data and software.

We introduce some diagnostics.  There are three kinds of diagnostics.

\begin{itemize}
\item First we have diagnostics based on morphology of the system.
  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
\begin{itemize}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  SW28), SQ for short-axis quads (as in Figure~SW02,
  SW09, SW29, SW42), IQ for inclined quads and CQ for very symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~SW05 and SW42) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~SW58,
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Second we have mass models, covered in Section~\ref{sec:massmodels}.
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  For SW36 the model implies extra images or a long arc,
  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth} and
  \ref{fig:encl}.
\end{itemize}
\item Third, whether the implied lensing mass is plausible, given the
  star-light in the lensing galaxy.  Section~\ref{sec:stellar-mass}
  explains how we compare the lensing mass with the mass in stars in
  the lensing galaxy.  We estimate the stellar mass by comparing
  galaxy magnitudes from the CFHTLS pipeline with the well-known
  stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
  extrapolate the stellar masses to a halo mass using the
  abundance-matching prescription of \cite{2010ApJ...710..903M}.
  Naturally, the lensing mass must be more than the stellar mass but
  no more than the total halo mass.  We then introduce what we call a
  halo index $\haloindex$ which gives an idea of how the lensing mass
  compares with these two bounds.  Figure~\ref{fig:stelmass}.
\end{itemize}

Section~\ref{sec:summary} summarises and tabulates the diagnostics in
Table~\ref{tab:models}.

The online supplement gives results for all the modelled systems.

### 2017-02-10 parts/summary.tex
editing text

>>>>

Collorative modelling\footnote{ See ``Collaborative gravitational lens
  modelling\dots'' in {\tt http://letters.zooniverse.org} $\{${\em
    Appears no longer available.}$\}$}
by volunteers.\footnote{In the
  main Space~Warps project for discovering lenses, volunteers in a
  crowd of $\gtrsim10^4$ make independent contributions.  Each person
  is presented with a random selection of survey-patches and invited
  to (in effect) vote on each.  The system estimates each volunteer's
  skill level according to test-patches interspersed with the real
  data, and weights their votes accordingly
  \citep{2016MNRAS.455.1171M}.  There is an active forum for
  volunteers, but since everyone is seeing different data samples with
  minimal overlap, the forum has little if any influence on votes.}
